\documentclass[11pt]{article}
\usepackage{geometry}
\geometry{a4paper, margin=0.75in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}

\usepackage{epigraph}

\usepackage{multicol}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}

\begin{document}

% 背景浮水印层 - 简化版本，更容易显示
\begin{tikzpicture}[remember picture, overlay]
    % 定义颜色
    \definecolor{watermarkblue}{RGB}{0, 122, 255}
    \definecolor{watermarkgray}{RGB}{142, 142, 147}
    \definecolor{watermarklight}{RGB}{200, 200, 220}
    
    % 设置透明度 - 更明显的透明度
    \tikzset{watermark/.style={opacity=0.15, thin}}
    
    % 简单的电路图案 - 左上角
    \begin{scope}[watermark, color=watermarkblue]
        \draw (0.5, 9.5) rectangle (2.5, 10.5);
        \draw (0.5, 9.5) -- (2.5, 9.5);
        \draw (0.5, 10) -- (2.5, 10);
        \draw (0.5, 10.5) -- (2.5, 10.5);
        \draw (1, 9.5) -- (1, 10.5);
        \draw (1.5, 9.5) -- (1.5, 10.5);
        \draw (2, 9.5) -- (2, 10.5);
        \fill (0.5, 9.5) circle (0.05);
        \fill (2.5, 9.5) circle (0.05);
        \fill (0.5, 10.5) circle (0.05);
        \fill (2.5, 10.5) circle (0.05);
    \end{scope}
    
    % 简单的大脑图案 - 右上角
    \begin{scope}[watermark, color=watermarkgray]
        \draw (6.5, 9.5) .. controls (7, 10) and (7.5, 10) .. (8, 9.5)
              .. controls (8.5, 9) and (8.5, 8.5) .. (8, 8)
              .. controls (7.5, 7.5) and (7, 7.5) .. (6.5, 8)
              .. controls (6, 8.5) and (6, 9) .. (6.5, 9.5);
        \draw (6.7, 9.3) -- (7.3, 9.1);
        \draw (6.8, 8.8) -- (7.2, 8.6);
        \draw (6.9, 8.3) -- (7.1, 8.1);
    \end{scope}
    
    % 简单的原子图案 - 左下角
    \begin{scope}[watermark, color=watermarklight]
        \fill (0.5, 1.5) circle (0.2);
        \draw[dashed] (0.5, 1.5) circle (0.8);
        \draw[dashed] (0.5, 1.5) circle (1.2);
        \fill (0.5, 2.3) circle (0.08);
        \fill (1.3, 1.5) circle (0.08);
        \fill (0.5, 0.7) circle (0.08);
        \fill (1.7, 1.5) circle (0.08);
    \end{scope}
    
    % 简单的芯片图案 - 右下角
    \begin{scope}[watermark, color=watermarkblue]
        \draw (6.5, 1.5) rectangle (8.5, 3.5);
        \draw (6.7, 1.7) rectangle (8.3, 3.3);
        \draw (6.5, 2) -- (6.3, 2);
        \draw (6.5, 2.5) -- (6.3, 2.5);
        \draw (6.5, 3) -- (6.3, 3);
        \draw (8.5, 2) -- (8.7, 2);
        \draw (8.5, 2.5) -- (8.7, 2.5);
        \draw (8.5, 3) -- (8.7, 3);
    \end{scope}
    
    % 简单的神经网络 - 中央
    \begin{scope}[watermark, color=watermarkblue]
        \fill (4, 6) circle (0.1);
        \fill (4, 5.5) circle (0.1);
        \fill (4, 5) circle (0.1);
        \fill (5, 6) circle (0.1);
        \fill (5, 5.5) circle (0.1);
        \fill (5, 5) circle (0.1);
        \fill (6, 5.5) circle (0.1);
        \draw (4, 6) -- (5, 6);
        \draw (4, 6) -- (5, 5.5);
        \draw (4, 6) -- (5, 5);
        \draw (4, 5.5) -- (5, 6);
        \draw (4, 5.5) -- (5, 5.5);
        \draw (4, 5.5) -- (5, 5);
        \draw (4, 5) -- (5, 6);
        \draw (4, 5) -- (5, 5.5);
        \draw (4, 5) -- (5, 5);
        \draw (5, 6) -- (6, 5.5);
        \draw (5, 5.5) -- (6, 5.5);
        \draw (5, 5) -- (6, 5.5);
    \end{scope}
    
    % 简单的数学符号 - 分散分布
    \begin{scope}[watermark, color=watermarkgray]
        % 积分符号
        \draw (2, 7) -- (2, 8);
        \draw (1.8, 7) -- (2.2, 7);
        \draw (1.8, 8) -- (2.2, 8);
        
        % 求和符号
        \draw (7, 7) circle (0.2);
        \draw (6.8, 7) -- (7.2, 7);
        \draw (7, 6.8) -- (7, 7.2);
        
        % 矩阵
        \draw (3, 2.5) rectangle (4, 3.5);
        \draw (3.2, 2.5) -- (3.2, 3.5);
        \draw (3.4, 2.5) -- (3.4, 3.5);
        \draw (3.6, 2.5) -- (3.6, 3.5);
        \draw (3.8, 2.5) -- (3.8, 3.5);
        \draw (3, 2.7) -- (4, 2.7);
        \draw (3, 2.9) -- (4, 2.9);
        \draw (3, 3.1) -- (4, 3.1);
        \draw (3, 3.3) -- (4, 3.3);
    \end{scope}
    
    % 量子比特 - 中上方
    \begin{scope}[watermark, color=watermarklight]
        \draw (4, 8.5) circle (0.15);
        \draw (4.5, 8.5) circle (0.15);
        \draw (5, 8.5) circle (0.15);
        \draw[dashed] (4, 8.5) -- (4.5, 8.5);
        \draw[dashed] (4.5, 8.5) -- (5, 8.5);
    \end{scope}
\end{tikzpicture}

\begin{center}
    \LARGE \textbf{Kevin Ting-Kai Kuo}
\end{center}

\vspace{1em}

% \section*{Contact Information}
\begin{multicols*}{2}
    


% \columnbreak
% % \section*{Motto}
% \epigraph{Think different, connect the dots.}{\textit{Steve Jobs}}

% {\footnotesize I am familiar with solving\textbf{ classical and quantum optical models}, numerically/symbolically, for instance (but not limited to):
%     • Jaynes-Cumming model for two-photon strongly-correlated system. • Bosonic sampling approach to implement optical quantum computation • Using \textbf{FDTD} to simulate optical metamaterial camera lens in Tyrafos technology.\\}

% \hrule

\section*{Contact}
{\footnotesize
\begin{itemize}[noitemsep]
    \item \href{https://github.com/Kuo-TingKai}{\textbf{\textcolor{blue}{Github}}}
    \item \textbf{Phone:} +886-922-082-811
    \item \textbf{Email:} KaiCoCat@proton.me
    \item \href{https://medium.com/@nehsm30126}{\textbf{\textcolor{blue}{Medium}}}/\href{https://www.overleaf.com/read/xzdtxtgxtnby#49163b}{\textbf{\textcolor{blue}{article list}}} about science
    \item \href{https://kuo-tingkai.github.io/theorem-dream/}{\textbf{\textcolor{blue}{Interactive novel}}}/\href{https://kuo-tingkai.github.io/QM.THREE/}{\textbf{\textcolor{blue}{Quantum Animation}}}/\href{https://kuo-tingkai.github.io/BubbleBook/}{\textbf{\textcolor{blue}{Baby book}}}
\end{itemize}
}

\section*{Fast Navigation}
You can jump to \href{#software-dev}{\textbf{\textcolor{blue}{Software Development}}} and \href{#experience}{\textbf{\textcolor{blue}{Experience}}} section\\

\hrule

\section*{Technology Stack Dashboard}
\begin{center}
\begin{tikzpicture}[scale=0.5]
    % 定义颜色
    \definecolor{techblue}{RGB}{0, 122, 255}
    \definecolor{techgreen}{RGB}{52, 199, 89}
    \definecolor{techorange}{RGB}{255, 149, 0}
    \definecolor{techred}{RGB}{255, 59, 48}
    \definecolor{techpurple}{RGB}{175, 82, 222}
    \definecolor{techgray}{RGB}{142, 142, 147}
    
    % 编程语言技能条
    \node[anchor=west] at (-2, 4.0) {\textbf{Programming Languages}};
    
    \draw[fill=techgray!20] (-2, 3.2) rectangle (6, 3.4);
    \draw[fill=techblue] (-2, 3.2) rectangle (5.5, 3.4);
    \node[anchor=west] at (6.2, 3.3) {\small Python};
    
    \draw[fill=techgray!20] (-2, 2.4) rectangle (6, 2.6);
    \draw[fill=techblue] (-2, 2.4) rectangle (5.2, 2.6);
    \node[anchor=west] at (6.2, 2.5) {\small C/C++};
    
    \draw[fill=techgray!20] (-2, 1.6) rectangle (6, 1.8);
    \draw[fill=techgreen] (-2, 1.6) rectangle (4.8, 1.8);
    \node[anchor=west] at (6.2, 1.7) {\small JS/TS};
    
    \draw[fill=techgray!20] (-2, 0.8) rectangle (6, 1.0);
    \draw[fill=techgreen] (-2, 0.8) rectangle (3.8, 1.0);
    \node[anchor=west] at (6.2, 0.9) {\small Golang};
    
    \draw[fill=techgray!20] (-2, 0.0) rectangle (6, 0.2);
    \draw[fill=techgreen] (-2, 0.0) rectangle (3.6, 0.2);
    \node[anchor=west] at (6.2, 0.1) {\small PHP};
    
    \draw[fill=techgray!20] (-2, -0.8) rectangle (6, -0.6);
    \draw[fill=techorange] (-2, -0.8) rectangle (3.3, -0.6);
    \node[anchor=west] at (6.2, -0.7) {\small Rust};
    
    \draw[fill=techgray!20] (-2, -1.6) rectangle (6, -1.4);
    \draw[fill=techorange] (-2, -1.6) rectangle (3.0, -1.4);
    \node[anchor=west] at (6.2, -1.5) {\small Java};
    
    % 系统开发技能条
    \node[anchor=west] at (-2, -2.4) {\textbf{System Development}};
    
    \draw[fill=techgray!20] (-2, -3.2) rectangle (6, -3.0);
    \draw[fill=techgreen] (-2, -3.2) rectangle (5.3, -3.0);
    \node[anchor=west] at (6.2, -3.1) {\small Linux/Embedded};
    
    \draw[fill=techgray!20] (-2, -4.0) rectangle (6, -3.8);
    \draw[fill=techgreen] (-2, -4.0) rectangle (5.3, -3.8);
    \node[anchor=west] at (6.2, -3.9) {\small Stream/\textbf{FFmpeg}};
    
    \draw[fill=techgray!20] (-2, -4.8) rectangle (6, -4.6);
    \draw[fill=techgreen] (-2, -4.8) rectangle (5.0, -4.6);
    \node[anchor=west] at (6.2, -4.7) {\small Docker/Cloud};
    
    \draw[fill=techgray!20] (-2, -5.6) rectangle (6, -5.4);
    \draw[fill=techgreen] (-2, -5.6) rectangle (4.8, -5.4);
    \node[anchor=west] at (6.2, -5.5) {\small Telemetry/eBPF};
    
    \draw[fill=techgray!20] (-2, -6.4) rectangle (6, -6.2);
    \draw[fill=techorange] (-2, -6.4) rectangle (4.8, -6.2);
    \node[anchor=west] at (6.2, -6.3) {\small Database};
    
    % AI/ML 技能条
    \node[anchor=west] at (-2, -7.2) {\textbf{AI/ML Technologies}};
    
    \draw[fill=techgray!20] (-2, -8.0) rectangle (6, -7.8);
    \draw[fill=techpurple] (-2, -8.0) rectangle (5.8, -7.8);
    \node[anchor=west] at (6.2, -7.9) {\small TF/keras/torch/jax};
    
    \draw[fill=techgray!20] (-2, -8.8) rectangle (6, -8.6);
    \draw[fill=techblue] (-2, -8.8) rectangle (5.0, -8.6);
    \node[anchor=west] at (6.2, -8.7) {\small Quantum DL/Qiskit/Qutip};
    
    \draw[fill=techgray!20] (-2, -9.6) rectangle (6, -9.4);
    \draw[fill=techgreen] (-2, -9.6) rectangle (4.5, -9.4);
    \node[anchor=west] at (6.2, -9.5) {\small Audio signal processing};
    

    

\end{tikzpicture}
\end{center}

\section*{Experience}\label{experience}

\subsection*{Senior engineer, IKG Team, 2024 Sep. - now}
\begin{itemize}[noitemsep]
    \item Develope browser-end multimedia player for video streams using \textbf{FFmpeg}, WebGPU,WebAssembly, 
    accelerating streams with \href{https://developer.nvidia.com/video-codec-sdk}{\textbf{\textcolor{blue}{NVIDIA encoder}}} 
    and customizing\textbf{ AI-masking frames} from \href{https://github.com/ossrs/srs}{\textbf{\textcolor{blue}{SRS}}} \textbf{ mediaserver}. 
    One of the features is parsing \textbf{unixtime} values embedded in \textbf{H.264 SEI} fields by \textbf{FFmpeg} at the streaming end from the player's decoder side, 
    used for synchronizing game states across different servers worldwide for the same game. 
    In the player design, utilized \textbf{WebRTC} protocol \textbf{STUN} related technologies to obtain players' real public IP information from their browser end, 
    serving as the basis for real-time monitoring and analysis of streaming quality across global regions. 
    Fine-tuned the player's \textbf{jitter buffer} during the player design process to optimize streaming latency issues
    \item \textbf{Monitoring/Logging/Telemetry} for network TTFF/latency with Grafana/Prometheus on AWS, 
    google analytics, Sentry (Python/Javascript SDK) \textbf{on cloud server}. 
    Built private cloud monitoring infrastructure for all on-premise and cloud servers and connected devices in Taipei and Europe, including multiple \textbf{ZCAM cameras} used for streaming, using \textbf{Grafana dashboards} with data sources from \textbf{Prometheus/Loki/Telegraf/Zabbix}
    \item Authentication for stream requests
    \item Serial port communication (USB, RS232) for game machine \textbf{micro-controller(MCU)}
    \item \href{https://www.byteplus.com/en/product/tos}{\textbf{\textcolor{blue}{Object storages}}} for \href{https://www.byteplus.com/en/product/vod}{\textbf{\textcolor{blue}{VODs}}} with \href{https://www.tencent.com/en-us/cloud}{\textbf{\textcolor{blue}{Tencent}}}/\href{https://www.byteplus.com/en/product/vod}{\textbf{\textcolor{blue}{BytePlus}}} cloud services
    \item Websockets/MQTT for game state machine message passing to Database (\textbf{PostgreSQL, MongoDB})
    \item Monte Carlo for event stochastic process outcome simulations.
    \item Technology stacks: Python/C++/\\Typescript/JavaScript/Go 
    \item Documenting with \textbf{Confluence}
    \item \textbf{Co-working with Europe team} for game projects without obstacles
\end{itemize}

\vspace{0.8em}

\subsection*{Senior engineer, Arcadyan Technology Co. Ltd., 2023 Dec.- 2024 July }
\begin{itemize}[noitemsep]
    \item \href{https://source.android.com/docs/compatibility/cts}{\textbf{\textcolor{blue}{Google xTS}}} test suite for \href{https://www.arcadyan.com/zh-hant/solutions/idea/stb/}{\textbf{\textcolor{blue}{Android TV}}} development, deployed and ran on Ubuntu Linux server
    \item Test automation cluster build-up (24-48 physical devices) for passing over 1-million test cases nightly by \textbf{sharding}.
    \item \textbf{Leadership:} Dispatch/Schedule remote contractors to complete a xTS test suite cycle per week
    \item \textbf{OTA/eMMC firmware update}
\end{itemize}

\vspace{0.8em}

\subsection*{Senior engineer, Marvell Technology Co. Ltd., 2023 Jan.-Dec.}
\begin{itemize}[noitemsep]
    \item \href{https://www.marvell.com/embedded-processors/armada-cp/}{\textbf{\textcolor{blue}{SSD NVMe controller}}} protocol front-end test/simulation tool development/test for \textbf{SSD controller firmware}, including device enumeration,function level hot reset features\textbf{ for cloud server storage}
    \item Test tool GUI development with PySide2
    \item Used qTest for regression test documenting, Jfrog for constructing CI upstream and software release. CI/CD and release.Wrote Java/Groovy/Shell scripts for CI/CD code on Jenkins.
    \item Docker/Manylinux to make software release more portable
    \item Slack/Jira for agile development
\end{itemize}

\vspace{0.8em}

\subsection*{Software Freelancer, 2022 Sep.-Dec.}
\begin{itemize}[noitemsep]
    \item AI pose detection for body training posing correction with PoseNet.
\end{itemize}

\vspace{0.8em}

\subsection*{\textbf{Algorithm engineer}, Tyrafos Technology, 2022 Mar.-Jul.}
\begin{itemize}[noitemsep]
    \item Real-time face recognition/fingerprint verification on embedded devices using neural network quantization in \textbf{TF-lite}
    \item Real-time Image signal processing (\textbf{ISP}) such like \textbf{HDR}, \textbf{3A} on mobile camera in \textbf{OpenCV}
    \item Optical \textbf{TRNG} encryption module on mobile phones obeying \textbf{NIST} entropy extraction test suite
\end{itemize}

\vspace{0.8em}

\subsection*{Full-stack engineer and Co-founder, Eunomia (a legal-tech startup), 2020 Jul.- 2022 Jan.}
\begin{itemize}[noitemsep]
    \item Build-up the \href{https://github.com/Kuo-TingKai/Eunomia}{\textbf{\textcolor{blue}{GUI}}} of a document editor with \textbf{Sequence-to-Sequence} model with \textbf{PyTorch} for \textbf{NLP} core, for the purpose of collaboration with lawyers and other workers in legal industry. Our WebUI was implemented with \textbf{Vue.js}/\textbf{Quill.js}, deployed on \textbf{GCP}/\textbf{Firebase}.
    \item Obtained the 2nd place in the 1st \textbf{Lawsnote Legaltech Hackathon}, 2020, Taiwan.
    \item Assisted by \textbf{NCCU} innovation center start-up incubator.
\end{itemize}

\hrule

\section*{Skills}
% A brief summary of your skills, exper, ience, and career goals.
\subsection*{Programming Languages}
% Todo 替以下Rust加上此超連結 https://github.com/xiph/rav1e/compare/master...Kuo-TingKai:rav1e:master
\begin{itemize}[noitemsep]
    \item \href{https://github.com/Kuo-TingKai/submarine-cable-monitor}{\textbf{\textcolor{blue}{Python}}}, 
    \href{https://github.com/Kuo-TingKai/cpp_linux_chat}{\textbf{\textcolor{blue}{C/C++}}}, 
    \href{https://github.com/Kuo-TingKai/three-3d-game}{\textbf{\textcolor{blue}{Javascript/Typescript}}}, 
    \href{https://github.com/Kuo-TingKai/golang-web3-app}{\textbf{\textcolor{blue}{Golang}}},
    \href{https://github.com/xiph/rav1e/compare/master...Kuo-TingKai:rav1e:master}{\textbf{\textcolor{blue}{Rust}}},
    \href{https://github.com/Kuo-TingKai/java-backend-cloud-maven-app}{\textbf{\textcolor{blue}{Java}}}, 
    \href{https://github.com/Kuo-TingKai/lean4-basic-ag}{\textbf{\textcolor{blue}{Lean}}}, PHP, 
    \href{https://github.com/Kuo-TingKai/RoR-app}{\textbf{\textcolor{blue}{Ruby on Rails}}}, 
    Julia, Shell scripts, Mathematica, R
\end{itemize}

\subsection*{Working OS Platforms}
\begin{itemize}[noitemsep]
    \item Ubuntu Linux, CentOS Linux, Android Linux, RaspberryPi OS, Windows
\end{itemize}

\subsection*{DL/ML/HPC/Statatistics}

\subsubsection*{DL Frameworks/AI compiler}
\begin{itemize}[noitemsep]
    \item \textbf{Tensorflow}:\href{https://github.com/Kuo-TingKai/TNNN}{\textbf{\textcolor{blue}{TF}}}/\textbf{TF-lite}/\\\textbf{Tensornetwork}/\textbf{Tensorboard}/\\\textbf{Tensorflow C++ API}\\
    \textbf{Jax}
    \item \textbf{Pytorch}: \textbf{torch}/\textbf{torch\_geometric}
    \item \textbf{ONNX}, \textbf{MLIR}
    \item HPC tools: \textbf{Pybind11}/\textbf{BLAS}/\textbf{OpenMP} 
\end{itemize}
\subsubsection*{Algorithms}
\begin{itemize}[noitemsep]
    \item ML/DL theory\\ Especially, I am sophisticated at a family of \textbf{physics-inspired} algorithms called \textbf{tensor network} (also called \textbf{tensor-train decomposition},TT, or \textbf{higher order singular value decomposition, HOSVD}), which are used in \textbf{LoRA} in the \textbf{LLM} field. 
    \item Image signal processing (\textbf{ISP}) \\
    Edge CV using pre-trained NN models then fine-tuned/migrate learning to in-firm data,\textbf{ quantized to FP int8 }and deployed on \textbf{RK3399 SoC} equipped with camera lens collaboratively RD with \textbf{FocalTech}, for the face verification system.\\
    \textbf{HDR} tonemapping, color space conversion for \textbf{CIS} camera lens \textbf{ISP} pipeline (with \textbf{OpenCV}). Spherical aberration calibration for the robotic vacuum. \\
    Circle/edge detection for the eye-moving instrument.  
    \item \href{https://github.com/Kuo-TingKai/IBMQcamp2020_VQE_team}{\textbf{Quantum Machine Learning}\\ quantum-classical\textbf{ hybrid CNN architecture}} implemented with Google \textbf{Qiskit}/\textbf{Tensorflow}/\textbf{Pannylane}/\textbf{Strawberryfield} running on \textbf{IBMQ} quantum server for solving the ground state energy of the molecule in the \textbf{IBMQ Quantum Computing Hackathon}.\\
    \item \textbf{Statistics}\\ multivariate time series such like \textbf{ARIMA} model, \textbf{VAR}, \textbf{GARCH} etc, with \textbf{ARIMA}(R) and \textbf{Statsmodel}(Python). Currently I am interested in the generalized version of \textbf{AIC}/\textbf{BIC} call \textbf{WAIC}/\textbf{WBIC} using algebraic statistics (algebraic geometry + statistics) invented by Watanabe, Riken.
    \item Numerical methods\\tensorization/\textbf{Monte Carlo}/\textbf{Quantum Monte Carlo}/\textbf{Markov Chain Monte Carlo}/\textbf{Simulated annealing} for solving combinatorical problem, e.g. the variant of travelling saleman problem (\textbf{TSP}) called \textbf{QAOA}, and physics problem ( phase transition classification and ground state solution).
    \item Cryptography: randomness(entropy) extraction, optical-based \textbf{TRNG} implemented by \textbf{LED} packaged on circuit for the electric network data transfer, which was inspired by \textbf{Samsung} mobile phone hardware encryption module.
\end{itemize}

\vspace*{-3em}
\section*{Software Development}\label{software-dev}

\begin{itemize}[noitemsep]
    \item Profiler: \textbf{perfetto}/\textbf{logcat}/\textbf{protobuf} on \textbf{Android Linux} platform.
    \item \textbf{Real time, Low latency System design on Linux}: \textbf{NVMe} \textbf{SSD} controller tool development and test 
    for several Linux distributions (\textbf{Ubuntu}/\textbf{CentOS}/\textbf{RPI}) using \textbf{Pybind11} 
    for binding top python API to C++ core library to call the \textbf{NVMe}/\textbf{PCIe} syscalls to the Linux kernel.
    Besides, we replaced the original ring buffer backend of  \textbf{NVMe} devices with \textbf{IOUring}/\textbf{Liburing} 
    for better I/O performance. Use Intel/WindRiver \href{https://www.windriver.com/products/simics}{\textbf{\textcolor{blue}{Simics}}} during the development and test.
    \item Web: \textbf{Vue}/\textbf{Node}/\textbf{Django}/\textbf{GCP}/\textbf{Firebase}
    \item Emulator/Simulator:\textbf{Qemu}(open-source)/\\\textbf{AVD}(\textbf{Android})/\textbf{Simics}(Windriver) for \textbf{SSD} device development and test.
    \item GUI: \textbf{PyQt5}, \textbf{PySide2}
    \item \textbf{Cloud Container virtualization}:\textbf{Docker} and \textbf{Docker-compose}, \textbf{LXC}(Linux generic container technology), \textbf{Proxmox}
    \item \textbf{OpenTelemetry} for monitoring/logging/telemetry:\\ \textbf{Prometheus}/\textbf{Grafana}/\textbf{Datadog}/\textbf{Sentry}
\end{itemize}

\vspace*{-3em}
\section*{Test}
\begin{itemize}[noitemsep]
    \item \textbf{Database: PostgreSQL, MongoDB}
    \item Agile: \textbf{Scrum}, \textbf{Jira}
    \item CI/CD: \textbf{Jenkins}/\textbf{Groovy}/\textbf{Git} action
    \item Test automation framework: \textbf{Pytest}/\textbf{Postman}/\\\textbf{Selemium}
\end{itemize}

\hrule

\columnbreak

\section*{Education}

\subsection*{BA, Economics, National Chengchi University, 2016-2018}

    \begin{itemize}[noitemsep]
        \item RA (Ministry of Science and Technology), Taiwan Policy Center, 2017-2018
        \item Graduate/undergraduate maths courses: advanced calculus, stochastic process, advanced probability, stochastic PDE (2016 summer school, NTU), differential geometry
        \item Graduate/undergraduate econ courses: Financial time series, Econometrics, Game theory, Macroeconomics, Microeconomics
        \item TWSIAM conference 2018, poster paper, forecasting for win rate of NBA teams using HMM model with Dirichlet prior implemented by R
    \end{itemize}


\subsection*{MA, Economics, National Chengchi University, 2018-2019 (incomplete)}

    \begin{itemize}[noitemsep]
        \item ICAPE 2020 Conference (San Diego), oral presentation: \href{https://ah.lib.nccu.edu.tw/item?item_id=163948&locale=en}{\textit{Shinn-Shyr Wang, Ting-Kai Kuo and Wen-Chieh Lee, National Chengchi University: Combating thick polar networks: is there any effective way other than the strategic network formation?}} Contribution: theoretical proof/numerical simulation for studying opinion convergence speed of manipulated social networks with echo-chamber effect implemented by Networkx and Numpy. I also set-up a manipulated chatroom with Node.js and Firebase providing for experimenters to use and monitored the opinion dynamics from the back-end.
        \item TA, principle of economics, 2018 autumn
    
        \item \textbf{RA, Music and Culture Technology Lab, Institute of Information Science, Academia Sinica, 2019}: Music score learning using graph neural network and topological data analysis with Tensorflow, Scikit-learn, Librosa.
        
    \end{itemize}

\subsection*{MA, Applied Physics, National Chengchi University, 2019-2020 (incomplete, master thesis defense passed)}

    \begin{itemize}[noitemsep]
        \item RA, Condensed Matter Center, NTU/ Institute of Applied Physics, NCCU
        \item TA, computational physics, 2019 spring, teaching quantum Monte Carlo
        \item Research: tensorize neural networks on condensed matter physics and conventional supervised learning task (image recognition) implemented by Tensorflow/Keras/Tensornetwork
        \item Courses: quantum computing, quantum mechanics, statistical mechanics, computational physics
        \item Seminar project: implemented quantum exponential adder with qiskit in quantum computing course 
    \end{itemize}

\hrule

\section*{Math/Physics/TCS Research Interest}
\begin{itemize}[noitemsep]
    \item Mathematica/Sagemath(Python) for symbolic/numerical computation for the Mathematical Physics.
    \item Computer Automatic Proof in Lean4/Coq/\\Isabelle language.  
    \item \textbf{ Currently, I am working with Dr. \href{https://www.bing.com/search?q=en-jui+kuo&gs_lcrp=EgZjaHJvbWUqBggBEEUYOzIGCAAQRRg5MgYIARBFGDsyBggCEEUYOzIGCAMQRRg7MgYIBBAAGEAyBggFEAAYQDIGCAYQRRg9MgYIBxBFGDwyBggIEEUYPNIBCDE2NjVqMGoxqAIAsAIA&FORM=ANAB01&PC=HCTS}{Kuo, En-Jui (UMD)} and Dr. \href{https://scholar.google.com.hk/citations?user=38TPAxMAAAAJ&hl=en}{Kam, Chon-Fai (SUNY Buffalo)} with: (1) Mack polynomial in string theory and (2) Hyperdeterminant in quantum entanglement, respectively. }
\end{itemize}


\end{multicols*}

\end{document}
